### 2017-01-11 papers.tex
Made article into a report

\section{Papers}

% =============================================================================
\subsection{\texttt{IND\_007} - Data Mining Algorithms to Classify Students}

@@

\subsubsection{Comment}

@@

\subsubsection{Relevant Points}

@@

\subsubsection{Work From This Paper}

@@

% =============================================================================
\subsection{\texttt{IND\_008} - Discovering decision knowledge from web log
portfolio for managing classroom processes by applying decision tree and data
cube technology}

>>>>

\chapter{Papers}

% =============================================================================
\section{\texttt{IND\_007} - Data Mining Algorithms to Classify Students}

@@

\subsection{Comment}

@@

\subsection{Relevant Points}

@@

\subsection{Work From This Paper}

@@

% =============================================================================
\section{\texttt{IND\_008} - Discovering decision knowledge from web log
portfolio for managing classroom processes by applying decision tree and data
cube technology}
